\chapter*{Executive Summary}
Advancements in technology have paved a path towards a safer and more convenient lifestyle. The underpinning of many recent advances is the increasingly dynamic technology allowing for more general products to address many specific issues. Two such technologies are the multirotor drone and the software defined radio (SDR). This project combines SDR with drone technology for even greater possibilities. \par

Multirotor drones are cheap, small, quick, and agile, which has led to innovations across many industries in the past decade. Software defined radios are similarly bringing cheap, reconfigurable radio to the market. The combination of the highly maneuverable drone with the software defined radio allows for a unique style of triangulation. Samples are taken at multiple points sequentially instead of in parallel, which is only possible with a quickly moving device like a drone and targets that are moving relatively slowly, like a stationary Wi-Fi access point or lost hiker in the woods. \par

Through the research of prior art, it was determined that similar projects have been conducted on these individual technologies, but none with them combined. Examples of prior art are the Sensor Processing and Path Planning Framework for a Search and Rescue UAV Network \cite{path_planning_snr_mqp} and the Software Defined Radio Localization using 802.11-style Communications \cite{sdr_localization_mqp}. This provided that the research done in the project will be the foundation of future development. \par

The implementation of this system can be seperated into multiple blocks. These blocks consist of coding framework, drone control, spectrum sensing, spectrum localization, and transmission to ground. Due to the independence of the modular platform to the drone, the coding framework is used to describe the actions of the system dependent on the state of the drone. These actions consist of sensing, rotation, on board computing and transmission to ground. In terms of drone control, most commercial drones operate at 2.4GHz which is the targetted sensing spectrum for this project. This is an issue because of the possibility that the drone control signals can interfere with the signals that the antennas are receiving. Therefore the wireless cards have to be replaced so that these drones can operate at 5GHz, a different frequency to the sensing spectrum. To conduct spectrum sensing, the board had to be interfaced with the Universal Software Radio Peripheral hardware driver (UHD) to the Ettus board. This required knowledge of how these libraries worked and how information is parsed in order to perform matched filtering. For spectrum localization, the board had to also be interfaced with a Global Positioning System (GPS) that determines the device's location. To improve accuracy, the GPS was implemented with a Kalman Filter as localization is highly dependent on accurate position information. GNU Radio was used to trasmit and receive at a ground station at 900MHz. \par

The outcome is a 3DR Solo drone capable of carrying the platform to detect nearby wireless signals. The received data corresponds well with the tests conducted, however the obtained GPS values despite using the Kalman Filter are not reliable enough to accurately localize the signal. Once the GPS values are reliable enough, the Python script coded will be able to map and determine the most likely point of origin of the signal. The transmission to ground is viable in lab scenarios but has not been fully integrated into the system when flown due to a malfunctiong device. \par

The essential value holds in the documentation provided, as it can be used as guidelines for future development.